---
title: "CGIAR SRTM 250m Digital Elevation Model"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Hole-filled Shuttle Radar Topography Mission (SRTM) data

Hole-filled seamless SRTM data V4 aggregated to 250m (SRTM_SE_250m) were
downloaded using the _raster_ packages `getData()` function.

## Hole-filled Shuttle Radar Topography Mission (SRTM) data

Hole-filled seamless SRTM data V4 aggregated to 250m (SRTM_SE_250m) were
downloaded using the _raster_ packages `getData()` function.

```{r get_dem, eval = TRUE}
Oz_dem <- raster::getData(name = "alt", country = "AUS", mask = TRUE)
raster::plot(Oz_dem)
```

The SRTM data were saved for use as package data in _WINS_ so that it will not
need to be downloaded every time data are interpolated in the future.

```{r save_data, eval=TRUE}
save(Oz_dem, file = "../inst/extdata/Oz_dem.rda", compress = "bzip2")
```

Cleanup alt files in Rmd directory.

```{r cleanup, eval = TRUE}
unlink("AUS_msk_alt.grd")
unlink("AUS_msk_alt.gri")
unlink("AUS_msk_alt.vrt")
```

## References

Jarvis A., H.I. Reuter, A.  Nelson, E. Guevara, 2008, Hole-filled seamless SRTM
data V4, International  Centre for Tropical  Agriculture (CIAT), available from
http://srtm.csi.cgiar.org.

## System Information

```{r sysinfo, eval=TRUE}
sessioninfo::session_info()
```
