---
title: "CGIAR SRTM 250m Digital Elevation Model"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Hole-filled Shuttle Radar Topography Mission (SRTM) data

Hole-filled seamless SRTM data V4 aggregated to 250m (SRTM_SE_250m) were
downloaded using the _raster_ packages `getData()` function.

## Hole-filled Shuttle Radar Topography Mission (SRTM) data

Hole-filled seamless SRTM data V4 aggregated to 250m (SRTM_SE_250m) were
downloaded using the _raster_ packages `getData()` function.

```{r get_dem, eval = TRUE}
# fetch DEM
Oz_dem <- raster::getData(name = "alt", country = "AUS", mask = TRUE)

# crop to remove islands
Oz_dem <- raster::crop(Oz_dem, raster::extent(114, 155, -45, -9))

# plot to check
raster::plot(Oz_dem)
```

The SRTM data were saved as a GeoTIFF file for use as package data in _WINS_ so
that it will not need to be downloaded every time data are interpolated in the
future.

```{r save_data, eval=TRUE}
raster::writeRaster(Oz_dem, filename = "../inst/extdata/Oz_dem",
                    overwrite = TRUE)
```

Cleanup alt files in Rmd directory.

```{r cleanup, eval = TRUE}
unlink("AUS_msk_alt.grd")
unlink("AUS_msk_alt.gri")
unlink("AUS_msk_alt.vrt")
```

## References

Jarvis A., H.I. Reuter, A.  Nelson, E. Guevara, 2008, Hole-filled seamless SRTM
data V4, International  Centre for Tropical  Agriculture (CIAT), available from
http://srtm.csi.cgiar.org.

## System Information

```{r sysinfo, eval=TRUE}
sessioninfo::session_info()
```
