---
title: "CGIAR SRTM 250m Digital Elevation Model"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Hole-filled Shuttle Radar Topography Mission (SRTM) data

Hole-filled seamless SRTM data V4 aggregated to 250m (SRTM_SE_250m) available
from <http://srtm.csi.cgiar.org> were downloaded from <https://drive.google.com/drive/u/0/folders/0B_J08t5spvd8VWJPbTB3anNHamc> and
uncompressed externally.

After extracting the GeoTIFF file, it was imported into R.

```{r, eval = TRUE}
Oz_dem <- raster::raster("~/Downloads/SRTM_SE_250m_TIF/SRTM_SE_250m.tif")
raster::plot(Oz_dem)
```

The SRTM data were cropped and masked for Australia only to remove unnecessary
data, using GADM data available through the
[_raster_](https://CRAN.R-project.org/package=raster ) package.

Due to islands, etc. the GADM data, `Oz_shape`, is cropped, then the `Oz_dem`
is cropped and masked using the `Oz_shape`.

```{r, eval=TRUE}
Oz_shape <- rnaturalearth::ne_countries(scale = 50,
                                        country = "Australia")

# Crop Oz_shape down to mainland only
Oz_shape <- raster::crop(Oz_shape, c(108,
                                     155,
                                     -45,
                                     -9))
Oz_dem <- raster::crop(Oz_dem, Oz_shape)
Oz_dem <- raster::mask(Oz_dem, Oz_shape)
raster::plot(Oz_dem)
```

SRTM data for Australia were saved as a package file for use in interpolating
temperature values.

```{r, eval=TRUE}
devtools::use_data(Oz_dem, internal = TRUE)
```

## References

Jarvis A., H.I. Reuter, A.  Nelson, E. Guevara, 2008, Hole-filled seamless SRTM
data V4, International  Centre for Tropical  Agriculture (CIAT), available from
http://srtm.csi.cgiar.org.